---
title: "oc2bioc -- notes for developers"
author: Vince Carey^[stvjc@channing.harvard.edu}
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{oc2bioc -- notes for developers}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Interacting with the open-cravat infrastructure

The `oc2bioc` package (currently at
github.com/vjcitn/oc2bioc) incorporates the open-cravat python modules.
In the main user vignette we invoke `populate_module_set`, to
learn about available modules in the OpenCRAVAT system.
The `oc2bioc` package will grow
to include formal interfaces to other key feature of OpenCRAVAT.

## Formal interfacing using basilisk

Let's have a look at `populate_module_set`:
```{r lklk}
library(oc2bioc)
populate_module_set
```

While this structure may appear complex, it is
schematic and easily thought of as a template.  The purpose
of the basilisk package functions is isolation of the 
open-cravat code and its dependencies to a mutually
consistent environment.

## Informal view of capabilities of the python stack using reticulate

In order to understand the features of the open-cravat
python stack, we can use reticulate on any system in which
open-cravat is installed and accessible via PYTHONPATH.

Below we see how to use reticulate to interrogate the `cravat`
module and its submodules from R.  There is a lot of software
in this stack.  Choosing functions to expose in R/Bioconductor
is a long-term project to be driven by user interest.

```
> library(reticulate)
1/5 packages newly attached/loaded, see sessionInfo() for details.
> cr = import("cravat")
> names(cr)
 [1] "admin_util"             "aggregator"             "BadFormatError"        
 [4] "base_annotator"         "base_commonmodule"      "base_converter"        
 [7] "base_mapper"            "base_postaggregator"    "BaseAnnotator"         
[10] "BaseCommonModule"       "BaseConverter"          "BaseMapper"            
[13] "BasePostAggregator"     "config_loader"          "ConfigLoader"          
[16] "ConfigurationError"     "constants"              "Cravat"                
[19] "cravat_class"           "cravat_filter"          "cravat_report"         
[22] "cravat_util"            "CravatFilter"           "CravatProfileException"
[25] "CravatReport"           "crx_def"                "exceptions"            
[28] "ExpectedException"      "FileIntegrityError"     "get_live_annotator"    
[31] "get_live_mapper"        "get_module"             "get_ucsc_bins"         
[34] "get_wgs_reader"         "inout"                  "InvalidData"           
[37] "InvalidReporter"        "KillInstallException"   "LiftoverFailure"       
[40] "LiveAnnotator"          "mp_runners"             "raise_break"           
[43] "reverse_complement"     "run"                    "run_reporter"          
[46] "signal"                 "store_utils"            "switch_strand"         
[49] "translate_codon"        "util"                   "wgs"                   
> cr$admin_util
Module(cravat.admin_util)
> head(names(cr$admin_util))
[1] "change_password" "check_login"     "compare_version" "constants"      
[5] "copy"            "create_account" 
```

## Interacting with the REST API for local deployments

See the documentation for `queryOC` in the `oc2bioc` package for
information on how RESTful queries can be resolved with locally
installed annotators.
